### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

\vspace{0.5ex}
Observe that \inc handles pattern/data updates in a unified way. Better still, it holds a nice property as follows.

\begin{theorem}
\label{thm-framework-inc}
With $\tilde{M}(P,G)$ and \fb \wrt an $h$-fragmentation of $P$, given $\Delta P$ and $\Delta G$,
the incremental algorithm \inc processes $\Delta P$ and $\Delta G$ in time
determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
\end{theorem}

We shall prove Theorem~\ref{thm-framework-inc} by providing specific techniques for \inc and analyzing its time complexity in Section~\ref{sec-IncAlg}.

>>>>

Observe that \inc handles pattern and data updates, separately and simultaneously, in a unified way.

### 2017-09-30 TF-vldb2018/subsec-auxstr.tex

%Algorithm \inc updates and uses \bfc in step (1) for identifying \affballsx for pattern updates.
\vspace{0.5ex}
\etitle{(2) Update planner (\upl)} consists of $h+1$ stacks $T({P}_{f1})$, $\ldots$, $T({P}_{fh})$, $T(C)$.
Stack $T(P_{fi})$ $(i\in [1,h])$ (resp. $T(C)$) records all unit updates in all arrived pattern updates $\Delta P_1$, $\ldots$, $\Delta P_{N}$ that are applied to fragment $P_{fi}$ (resp. $C$) of $P$.
Initially, all of them are empty.
They are dynamically updated for each unit update in each set of coming pattern updates.
\looseness=-1

>>>>

%Algorithm \inc updates and uses \bfc in step (1) for identifying \affballsx for pattern updates.
\vspace{0.5ex}
\etitle{(2) Update planner (\upl)} consists of $h+1$ stacks $T({P}_{f1})$, $\ldots$, $T({P}_{fh})$, $T(C)$.
Stack $T(P_{fi})$ $(i\in [1,h])$ (resp. $T(C)$) records all unit updates in all arrived pattern updates $\Delta P_1$, $\ldots$, $\Delta P_{N}$ that are applied to fragment $P_{fi}$ (resp. $C$) of $P$.
Initially, all of them are empty.
They are dynamically updated for each unit update in each set of coming pattern updates.

Better still, it holds a nice property as follows.
\begin{theorem}
\label{thm-framework-inc}
With $\tilde{M}(P,G)$ and \fb \wrt an $h$-fragmentation of $P$, given $\Delta P$ and $\Delta G$,
the incremental algorithm \inc processes $\Delta P$ and $\Delta G$ in time
determined by $P$, $\tilde{M}(P,G)$ and \affballsx, not directly depending on $G$.
\end{theorem}

We shall prove Theorem~\ref{thm-framework-inc} by providing specific techniques for \inc and analyzing its time complexity in Section~\ref{sec-IncAlg}.
